---
title: "Computing the MSE when errors are Normal Distributed"
author: "Ali Al-Sharadqah, Nicholas Woolsey, Ola Nusierat"
date: '`r Sys.Date()`'
date: "`r Sys.Date()`"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This code generates Figures 1-3 for the normal error case. You need to change the setting to generate all figures as described below.

#### MALS Code

This code to compute the slope using MALS method.

Input: The covariate (x), the response data (y), and the $\sigma_{\delta_i}^2$, $\sigma_{\epsilon_i}^2$, and $\sigma_{\delta_i\epsilon_o}$. 

Outpout: The estimate the slope $\beta$.

```{r MALS}
options(digits = 3)
library(RConics)
library(mvtnorm)
library(geigen)

MALS <- function(data,sigmadelta,sigmaeps,sigmadeltaeps)
{
  #modified least squares
  n <- length(data)/2;  x <- data[1:n]; y <- data[(n+1):(2*n)]
  ti <- matrix(cbind(rep(1,n),x), ncol = 2 )  
  h0i <- matrix(cbind(y,x*y), ncol = 2 )  
  hi <- cbind(y,x*y-sigmadeltaeps)
  tt <- matrix(c(1,mean(ti[,2]), mean(ti[,2] ), mean(ti[,2] * ti[,2]) ), ncol=2, nrow=2)
  H <- matrix(c(1, mean(x), mean(x), mean(x^2-sigmadelta)), nrow = 2,ncol = 2)
  Lambda.bar <-  tt - H
  h.bar <- matrix(c( mean(y), mean(x * y) - mean(sigmadeltaeps) ), ncol = 1, nrow = 2)
  v.bar <-   apply(ti*y  ,2,mean )-h.bar
  cc0 <- y%*%ti/n;  cc1 <- matrix(c(mean(y^2), cc0), ncol =1)
  
  A <- matrix( cbind(cc1, rbind(cc0,H  )),nrow=3,ncol=3); A<- (A+t(A))/2
  bb1 <- matrix(c(mean(sigmaeps),  v.bar), nrow=1, ncol=3)
  bb2 <- matrix( c( t(v.bar), Lambda.bar) ,nrow = 2,ncol = 3)
  
  B <- matrix(rbind( bb1,bb2),nrow=3,ncol=3); B<- (B+t(B))/2
  w <- solve(A)%*%B; w <- (w + t(w) ) /2
  sols <-  geigen(  B,A,symmetric= FALSE)$values
  if(length(sols)==0){                 return(c(NA,NA)) }
  else
  {
    lambda<-  max( sols  )#%[which(sols == min(sols))]#if there are real positive solutions
    alp<-1
    a<- ifelse( lambda > 1+1/n, (n - alp) /n, lambda * (n - alp )/(n + 1))
    thetahat <-  solve(tt - a * Lambda.bar) %*% matrix((  matrix(apply(h0i,2,mean),ncol=1) -  v.bar),ncol=1)  #return betahat from paper
    return(thetahat[2] )
  }
}
```

## MALS Code

This code to compute the slope using MCS method.

Input: The covariate (x), the response data (y), and the $\sigma_{\delta_i}^2$, $\sigma_{\epsilon_i}^2$, and $\sigma_{\delta_i\epsilon_o}$. 

Outpout: The estimate the slope $\beta$.

```{r MCS}
 
MCS  <- function(data,sigmadelta,sigmaeps,sigmadeltaeps){
  n <- length(data)/2;  x <- data[1:n]; y <- data[(n+1):(2*n)]
  ti <- cbind(rep(1,n),x)/sqrt(sigmaeps)    #notation is taken from paper
  yt <- matrix(c(sum(y/sigmaeps),sum(y*x/sigmaeps)), nrow=2)
  Mt <- t(ti)%*%ti
  Tt  <- matrix(c(sum(1/sigmaeps),sum(x/sigmaeps),sum(x/sigmaeps),sum((x^2-sigmadelta)/sigmaeps)),nrow=2,ncol=2)
  V  <- Mt - Tt
  V <-  (V + t(V) )/2
  cc1 <- matrix(c( sum(y^2/sigmaeps) , yt), ncol = 1 , nrow = 3)
  cc2 <- matrix( rbind( t(yt), Mt), nrow = 3 , ncol = 2 )
  A<- cbind( cc1 , cc2 )
  A <- (A + t(A) )/2
  B =matrix(0, nrow=3, ncol=3)
  B[2:3,2:3] <- V
  C <- solve(A)%*% B
  C <- (C+t(C))/2
  lamb0 <- (1/ eigen(C,only.values = TRUE)$values)
  lamb <-  min( lamb0[ which(lamb0>0) ] ) 
  a <- ifelse(lamb < 1 + 1/n,  lamb*(n-2)/(n+1) ,(n-2)/n )  
  thetahat<-solve(Mt-a*V)%*%yt
  
  return( thetahat[2])
}
```


## GLS Code
This code to compute the slope using GLS method.

Input: The covariate (x), the response data (y), and the $\sigma_{\delta_i}^2$, $\sigma_{\epsilon_i}^2$, and $\sigma_{\delta_i\epsilon_o}$. 

Outpout: The estimate the slope $\beta$.

```{r GLS}
 
WLS <- function(data,sigmadelta,sigmaeps,sigmadeltaeps)#weighted least squares
{      
  n <- length(data)/2
  x <- data[1:n]
  y <- data[(n+1):(2*n)]
  
  xstar <- x-mean(x)
  ystar <- y-mean(y)
  obj <- function(B)
  {
    phi <- sigmadelta*B^2-2*B*sigmadeltaeps + sigmaeps
    return(sum((ystar-B*xstar)^2/phi))
  }
  betahat <- optimize(f=obj,interval=c(-200,200))$minimum#same minimization as our method
  alphahat <- mean(y)-betahat*mean(x)
  return( betahat)
}
 
```

## Our Proposed Method Code
This code to compute the slope using our method.

Input: The covariate (x), the response data (y), and the $\sigma_{\delta_i}^2$, $\sigma_{\epsilon_i}^2$, and $\sigma_{\delta_i\epsilon_o}$. 

Outpout: The estimate the slope $\beta$.

```{r Ours}
 
Ours <- function(data, sigmadelta,sigmaeps,sigmadeltaeps)
{
  n <- length(data)/2
  x <- data[1:n]
  y <- data[(n+1):(2*n)]
  xstar <-x-mean(x)
  ystar <-y-mean(y)
  
  obj <- function(B) #objective function to minimize
  {
    phi <- sigmadelta*B^2-2*B*sigmadeltaeps+sigmaeps
    return(sum(xstar^2/phi)^(-1/(n-2))*sum((ystar-B*xstar)^2/phi))
  }
  betahat<- optimize(f=obj,interval=c(-1,3) )$minimum 
  alphahat<- mean(y) - betahat *mean(x)
  
 return( betahat )
  
}
```

##Generating error
This code generates  the variances of the error

Input: The $\bar{sigma}_{delta}$, the correlation coefficent $\rho$, sample size $n$, and Boolean varaiabel Cor (if error are uncorrelated use Cor=0 otherwise use Cor=F). Note that we used here $\lambda=2$. To reporduce other figures with different $\lambda$, change this one here.

Outpout: The estimate the slope $\hat{\beta}$.

```{r covariance}
CovMatrixGen1 <- function(sigx.bar ,rho, n,  Cor)
{
  ee <-  runif(n, -1/20,1/20)
  ee1 <- ee-mean(ee)
  SigX <- ( matrix(1, nrow=n, ncol=1)+ee1 )*sigx.bar^2
  lambda  <-  2 
  SigY <-  sigx.bar^2*matrix( lambda ,nrow=n, ncol=1)
  SigXY <-  matrix( rep(0,n), nrow=n, ncol=1)
  if(Cor==1)
  {
    bb <-runif(n, -0.05,0.05)
    bb1 <-bb-mean(bb)
    SigXY <- (rho + matrix(bb1, nrow=n, ncol=1))*sqrt(SigY*SigX)
  }
  
  Sigma <- cbind( SigX,  SigXY , SigY)
  return(Sigma)
}
```

## Main Code to makes figures 1-3. 
This codes computes the MSE for the four methods and graph them. Note Cor=F; thus this mean we deal with uncorrelated errors. If $Cor=T$ this will generate the MSE for correlated errors. 




```{r main}

samp <-  5*10^4
Cor <- F
rho <- 0.2* Cor
Lower <- 0;   Upper <- c(0.8,1,1,1) #lower bound and upper bound of the interval 


a <- 0.25  # The true value of the y-intercept (alpha) 
b <- 0.8        # The true value of the slope (beta)
theta <- c(a,b)

ns <-  c( 22,40 ,60,80 )    # sample sizes
size <-length(ns)
sigmas <-c(  0.005, 0.0075, 0.010, 0.025, 0.050, 0.075, 0.100, 0.125, 0.150, 0.200, 0.250, 0.300, 0.350, 0.4, 0.45, 0.5, 0.55 ,0.6,0.65,0.7,0.75,0.8)
M <- length(sigmas)

MseMM.Total  <- MseALS.Total   <- MseMALS.Total  <-  MseCS.Total  <- MseMCS.Total  <- MseWLS.Total  <- MseOurs.Total   <- c()

for(i in 1:size)
{
  n <- ns[i]
  MseMM  <- MseALS   <-  MseMALS   <- MseCS  <-  MseMCS   <- MseWLS   <-  MseOurs  <- c()
  Leng <- Upper[i] - Lower
  xi<- c()
  xi <- seq(Lower,Upper[i], Leng/(n-1))     #true x-values   
  Var.xi <- var(xi)
  print(Var.xi)
  print(n)
  
  for(sig in sigmas ) # these act as   
  {
    Sigma  <-  CovMatrixGen1( sig, rho, n,  Cor )
  #  print( kappa <-  Var.xi/( Var.xi+sig^2) )
    delta <- eps <- S <- c()
    
    for(i in 1:n)  # generate the errors
    {
      
      S     <-  matrix( c( Sigma[i,1], Sigma[i,2], Sigma[i,2], Sigma[i,3] ), nrow = 2 , ncol = 2 ) 
      temp  <- rmvnorm( samp, mean = c(0,0), S )
      delta <- rbind( delta, temp[,1] ) 
      eps   <- rbind( eps, temp[,2] )
    }
    
    x <- matrix(xi, nrow = n, ncol = samp ) + delta # observed x
    y <- a+ x * b + eps # observed y
    data   <- rbind(x ,y)          
    
    
    ######################################################################################
    #   apply methods for all data of size sample: note each sample is a row in data 
    #   The x values are the first n rows while the y values the last n rows. This will give 
    # the MSE  for all values of sigma
    # ######################################################################################
    
    ##  MALS
    mals      <- apply(data,2, MALS, sigmadelta = Sigma[,1],sigmaeps = Sigma[,3], sigmadeltaeps = Sigma[,2] ) 
    MseMALS <- append(MseMALS, mean((mals - theta[2] )^2   )   )

    # MCS
    mcs     <- apply(data, 2, MCS, sigmadelta = Sigma[,1],sigmaeps = Sigma[ ,3], sigmadeltaeps = Sigma[ ,2])
    MseMCS<- append(MseMCS, mean((mcs- theta[2])^2 )   )

    ##  WLS
    wls      <- apply(data,2, WLS, sigmadelta=Sigma[,1],sigmaeps=Sigma[,3],sigmadeltaeps=Sigma[,2])
    MseWLS <- append(MseWLS, mean((wls - theta[2])^2 )       )

    # Ours
    ours    <- apply(data,2, Ours, sigmadelta = Sigma[,1],sigmaeps = Sigma[ ,3],sigmadeltaeps = Sigma[ ,2])
    MseOurs<- append(MseOurs, mean((ours - theta[2])^2 )  )

    
  }
 
  MseMALS.Total<-rbind(MseMALS.Total,MseMALS )
  MseMCS.Total<-rbind(MseMCS.Total,MseMCS )
  MseWLS.Total <- rbind(MseWLS.Total, MseWLS )
  MseOurs.Total <- rbind(MseOurs.Total,MseOurs  )
  
}
```

## Plotting
```{r plotting}

par(mfrow=c(2,2),mar=c(4.5,4.5,2,2),font.axis=2,cex.lab=1.9,cex.main=1.5) 

plot(sigmas,MseOurs.Total[1,], main="n=20" , col="blue", lwd=3, xlim=c(min(sigmas),0.8), ylim=c(min(MseOurs.Total[1,]),1.2),  xlab = expression(paste(bold(sigma)[epsilon])), ylab=bquote(bold('MSE')),  type = "l" )
lines(sigmas,MseWLS.Total[1,] , col="black", lwd=3)
lines(sigmas,MseMALS.Total[1,] , col="red", lwd=3)
lines(sigmas, MseMCS.Total[1,] , col="darkgreen",lwd=3 )

legend("bottomrigh",l,legend=c(as.expression(bquote(bold("MALS"))),bquote(bold('GLS') ),bquote(bold('MCS')),bquote(bold('Proposed'))), col=c('red', 'black','darkgreen','blue'),lwd=5, cex=1,box.lty=0 )


plot(sigmas,MseOurs.Total[2,], main="n=40" , col="blue", lwd=3, xlim=c(min(sigmas),0.8), ylim=c(min(MseOurs.Total[1,]),1.2),  xlab = expression(paste(bold(sigma)[epsilon])), ylab=bquote(bold('MSE')),  type = "l" )
lines(sigmas,MseWLS.Total[2,] , col="black", lwd=3)
lines(sigmas,MseMALS.Total[2,] , col="red", lwd=3)
 lines(sigmas, MseMCS.Total[2,] , col="darkgreen",lwd=3 )


plot(sigmas,MseOurs.Total[3,], main="n=60" , col="blue", lwd=3, xlim=c(min(sigmas),0.8), ylim=c(min(MseOurs.Total[1,]),1.2),  xlab = expression(paste(bold(sigma)[epsilon])), ylab=bquote(bold('MSE')),  type = "l" )
lines(sigmas,MseWLS.Total[3,] , col="black", lwd=3)
lines(sigmas,MseMALS.Total[3,] , col="red", lwd=3)
lines(sigmas, MseMCS.Total[3,] , col="darkgreen",lwd=3 )


plot(sigmas,MseOurs.Total[4,], main="n=80" , col="blue", lwd=3, xlim=c(min(sigmas),0.8), ylim=c(min(MseOurs.Total[1,]),1.2),  xlab = expression(paste(bold(sigma)[epsilon])), ylab=bquote(bold('MSE')),  type = "l" )
lines(sigmas,MseWLS.Total[4,] , col="black", lwd=3)
lines(sigmas,MseMALS.Total[4,] , col="red", lwd=3)
lines(sigmas, MseMCS.Total[4,] , col="darkgreen",lwd=3 )

```
